Pteropod biomarker analysis

### 2018-04-18 figures.Rmd
mod tables added

---
output:
  html_document:
    keep_md: yes
    self_contained: no
    code_folding: hide
---

@@

```{r echo = T, message = F, warning = F}
library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(knitr)
library(gridExtra)
library(grid)

@@

```
Fig. 3 Examples of model interactions of co-occuring environmental variables on cellular response measures.  Each subplot shows a different relationship as either additive or synergistic effects between the variables. All y-axes are transformed to conform to model output. Covarying environmental variables were held constant at the minimum, 25th, median, 75th, and maximum values in the observed data.

@@

grid.arrange(p4, p5, ncol = 2)
```
Fig. 4 Examples of model interactions of co-occuring environmental variables on abundance and shell dissolution. Each subplot shows a different relationship as either additive or synergistic effects between the variables. All y-axes are transformed to conform to model output. Covarying environmental variables were held constant at the minimum, 25th, median, 75th, and maximum values in the observed data.

```{r, eval = F}
mods <- readxl::read_excel('raw/info for table.xlsx') %>% 
  .[-1, -1] %>% 
  gather('var', 'Model', everything()) %>% 
  mutate(
    org = ifelse(var %in% c('abundance', 'dissolution', 'length'), 'phy', 'bio'),
    Model = paste0('mod', Model)
    ) %>% 
  split(.$org)

biotab <- mods$bio %>% 
  left_join(biomod, by = 'Model') %>% 
  select(Model, data) %>%
  mutate(data = map(data, function(x){
    x %>% mutate(vr = seq(1:nrow(.)))
  })) %>% 
  unnest %>% 
  mutate(
    Model = gsub('mod', '', Model),
    Model = as.numeric(Model)
    ) %>% 
  group_by(Model) %>% 
  mutate(
    Pvl = gsub('ns', '', Pvl), 
    Rsq = ifelse(duplicated(Rsq), '', Rsq)
    ) %>% 
  ungroup %>% 
  unite('Est', Est, Pvl, sep = '') %>% 
  gather('estnm', 'estvl', Rsq, Est) %>% 
  unite('est', pte_lab, estnm, sep = ', ', remove = F) %>% 
  select(-estnm) %>% 
  split(.$pte_lab) %>%
  lapply(., function(x){

    out <- spread(x, est, estvl) %>% 
      select(-pte_lab) %>%
      arrange(Model, vr) %>% 
      select(-vr, -Model)

    if(!any(grepl('^LPX', names(out))))
      out <- out %>% 
        select(-env_lab)

    return(out)

  }) %>% 
  do.call('cbind', .) %>% 
  mutate(
    Model = rep(letters[1:(nrow(.)/3)], each = 3),
    Model = paste0('(', Model, ')'),
    Model = ifelse(duplicated(Model), '', Model)
  ) %>% 
  select(Model, everything())

names(biotab) <- gsub('^.*\\.', '', names(biotab))
vrs <- gsub('(^.*),\\s.*$', '\\1', names(biotab))
vrs[duplicated(vrs)] <- ''
vrs <- paste0(vrs, '<br>')
vrs[vrs %in% 'env_lab<br>'] <- 'Parameter<br>'
vrs2 <- gsub('^.*,\\s|Model|env_lab', '', names(biotab))
vrs <- paste(vrs, vrs2, sep = '')

names(biotab) <- vrs

knitr::kable(biotab, caption = "Table 1: Model results for pteropod cellular response to pairs of co-occurring environmental variables. The estimated joint effects of variables in each model are shown.  The overall R-squred value for each model is also shown.  Significance of each effect is noted as * p < 0.05, ** p < 0.005.")
```

```{r, eval = F}
phytab <- mods$phy %>% 
  left_join(phymod, by = 'Model') %>% 
  select(Model, data) %>%
  mutate(data = map(data, function(x){
    x %>% mutate(vr = seq(1:nrow(.)))
  })) %>% 
  unnest %>% 
  mutate(
    Model = gsub('mod', '', Model),
    Model = as.numeric(Model)
  ) %>% 
  group_by(Model) %>% 
  mutate(
    Pvl = gsub('ns', '', Pvl), 
    Rsq = ifelse(duplicated(Rsq), '', Rsq)
  ) %>% 
  ungroup %>% 
  unite('Est', Est, Pvl, sep = '') %>% 
  gather('estnm', 'estvl', Rsq, Est) %>% 
  unite('est', pte_lab, estnm, sep = ', ', remove = F) %>% 
  select(-estnm) %>% 
  split(.$pte_lab) %>%
  lapply(., function(x){

    out <- spread(x, est, estvl) %>% 
      select(-pte_lab) %>%
      arrange(Model, vr) %>% 
      select(-vr, -Model)

    if(!any(grepl('^abu', names(out))))
      out <- out %>% 
        select(-env_lab)

    return(out)

  }) %>% 
  do.call('cbind', .) %>% 
  mutate(
    Model = rep(letters[1:(nrow(.)/3)], each = 3),
    Model = paste0('(', Model, ')'),
    Model = ifelse(duplicated(Model), '', Model)
  ) %>% 
  select(Model, everything())

names(phytab) <- gsub('^.*\\.', '', names(phytab))
vrs <- gsub('(^.*),\\s.*$', '\\1', names(phytab))
vrs[duplicated(vrs)] <- ''
vrs <- paste0(vrs, '<br>')
vrs[vrs %in% 'env_lab<br>'] <- 'Parameter<br>'
vrs2 <- gsub('^.*,\\s|Model|env_lab', '', names(phytab))
vrs <- paste(vrs, vrs2, sep = '')
vrs <- gsub('abu', 'Abundance', vrs)
vrs <- gsub('len', 'Length', vrs)
vrs <- gsub('dis', 'Shell dissolution', vrs)

names(phytab) <- vrs

knitr::kable(phytab, caption = "Table 2: Model results for pteropod physiological and population response to pairs of co-occurring environmental variables. The estimated joint effects of variables in each model are shown.  The overall R-squred value for each model is also shown.  Significance of each effect is noted as * p < 0.05, ** p < 0.005.")
```

>>>>

---
output:
  html_document:
    keep_md: yes
    self_contained: no
    code_folding: hide
    css: styles.css
---

<a href="https://github.com/fawda123/Pteropod_biomarker/" class="github-corner" aria-label="View source on Github"><svg width="80" height="80" viewBox="0 0 250 250" style="fill:#FD6C6C; color:#fff; position: absolute; top: 0; border: 0; left: 0; transform: scale(-1, 1);" aria-hidden="true"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a><style>.github-corner:hover .octo-arm{animation:octocat-wave 560ms ease-in-out}@keyframes octocat-wave{0%,100%{transform:rotate(0)}20%,60%{transform:rotate(-25deg)}40%,80%{transform:rotate(10deg)}}@media (max-width:500px){.github-corner:hover .octo-arm{animation:none}.github-corner .octo-arm{animation:octocat-wave 560ms ease-in-out}}</style>

@@

```{r echo = T, message = F, warning = F}
library(tidyverse)
library(vegan)
library(ggord)
library(scales)
library(effects)
library(knitr)
library(gridExtra)
library(grid)
library(stargazer)

@@

```
<!-- Fig. 3 Examples of model interactions of co-occuring environmental variables on cellular response measures.  Each subplot shows a different relationship as either additive or synergistic effects between the variables. All y-axes are transformed to conform to model output. Covarying environmental variables were held constant at the minimum, 25th, median, 75th, and maximum values in the observed data. -->

@@

grid.arrange(p4, p5, ncol = 2)
```
<!-- Fig. 4 Examples of model interactions of co-occuring environmental variables on abundance and shell dissolution. Each subplot shows a different relationship as either additive or synergistic effects between the variables. All y-axes are transformed to conform to model output. Covarying environmental variables were held constant at the minimum, 25th, median, 75th, and maximum values in the observed data. -->

```{r, eval = T, results = 'asis'}
biotab <- biomod %>% 
  unnest(data) %>% 
  group_by(Model) %>% 
  mutate(n = n()) %>% 
  filter(n > 1) %>% 
  dplyr::select(-n)
biotab <- filter(biomod, Model %in% unique(biotab$Model))

cap <- 'Table 1: Model results for pteropod cellular response to pairs of co-occurring environmental variables. The estimated joint effects of variables and their significance in each model are shown.  Parameter estimates with standard errors (in parentheses) are included with overall model statistics (R-squared, F statistic) at the bottom. Models with the same cellular response measure can be identified with the column names at the top.'

stargazer(biotab$Modobj, type = 'html', title = cap, digits = 2, keep.stat = c('adj.rsq'), intercept.top = T, intercept.bottom = F, dep.var.caption = 'Cellular response measures')
```

```{r, results = 'asis'}
phytab <- phymod %>% 
  unnest(data) %>% 
  group_by(Model) %>% 
  mutate(n = n()) %>% 
  filter(n > 1) %>% 
  dplyr::select(-n)
phytab <- filter(phymod, Model %in% unique(phytab$Model))

cap <- 'Table 2: Model results for physiological and abundance responses to pairs of co-occurring environmental variables. The estimated joint effects of variables and their significance in each model are shown.  Parameter estimates with standard errors (in parentheses) are included with overall model statistics (R-squared, F statistic) at the bottom. Models with the same response measure can be identified with the column names at the top.'

stargazer(phytab$Modobj, type = 'html', title = cap, digits = 2, keep.stat = c('adj.rsq'), intercept.top = T, intercept.bottom = F, dep.var.caption = 'Physiological response measures', dep.var.labels = c('Abundance', 'Shell dissolution'))
